A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-06-29 tex/paper.tex
hdfcat

\paragraph{Test 2}: I think we should fit both an F/G star (WASP-14) and a K/M star (TBD) with both the Kurucz and PHOENIX spectra. This will show a few things
\begin{itemize}
  \item Spectral parameters can vary by a large margin depending on which spectral library you use ($200~K$ or more).
  \item Both spectral libraries have stars that they perform better and worse on.
  \item This will be reflected in the increased level of global noise, and number of ``bad'' regions that have been instantiated.
\end{itemize}

>>>>

\paragraph{Test 2}: I think we should fit an optical spectrum of an F star (WASP-14) and a near-IR spectrum of an M star (Gl51). The WASP will be fit with both the Kurucz and PHOENIX spectra, while the M star will be fit with just the PHOENIX. This will show a few things
\begin{itemize}
  \item Spectral parameters can vary by a large margin depending on which spectral library you use ($200~K$ or more).
  \item Both spectral libraries have stars that they perform better and worse on.
  \item This will be reflected in the increased level of global noise, and number of ``bad'' regions that have been instantiated.
\end{itemize}
